### 2018-04-06 Manuscript/chapter4.tex
Nutrition p

Honeybee declines have been associated with several factors, including pesticide use, parasites, pathogens, habitat loss, and poor nutrition (\citealt{factors}, \citealt{factors2}). Researchers generally agree that these stressors do not act in isolation; instead, they appear to influence the large-scale loss of honeybees in interactive fashions as the environment changes (\citealt{interacting}). Two factors that have posed heightened danger to honeybee health related to environmental changes are nutrition and viruses.

>>>>

Honeybee declines have been associated with several factors, including pesticide use, parasites, pathogens, habitat loss, and poor nutrition (\citealt{factors}, \citealt{factors2}). Researchers generally agree that these stressors do not act in isolation; instead, they appear to influence the large-scale loss of honeybees in interactive fashions as the environment changes (\citealt{interacting}). Nutrition and viral infection are two broad factors that pose heightened dangers to honeybee health in response to recent environmental changes.

Pollen is the main source of nutrition (including proteins, amino acids, lipids, sterols, starch, vitamins, and minerals) in honeybees (\citealt{source}, \citealt{source2}). At the individual level, pollen supplies most of the nutrients necessary for physiological development (\citealt{brodschneider}) and is believed to have considerable impact on longevity (\citealt{longevity}). At the colony level, pollen enables young workers to produce jelly, which then nourishes larvae, drones, older workers, and the queen (\citealt{jelly}, \citealt{jelly2}). Various environmental changes (including urbanization and monoculture crop production) have significantly altered the nutritional profile available to honeybees. In particular, honeybees face less diverse selections of pollen, which is of concern because mixed-pollen (polyfloral) diets are generally considered healthier than single-pollen (monofloral) diets (\citealt{diverse}, \citealt{diverse2}, \citealt{diverse3}). Indeed, reported colony mortality rates are higher in developed land areas compared to undeveloped land areas (\citealt{undeveloped}), and beekeepers rank poor nutrition as one of the main reasons for colony losses (\citealt{bkLoss}). Understanding how undiversified diets affect honeybee health will be crucial to resolve problems that may arise as agriculture continues to intensify throughout the world (\citealt{ag}, \citealt{ag2}).
